Statistical analysis of periodic data in neuroscience

### 2021-01-04 manuscript/manuscript.Rmd
Update manuscript.Rmd

nsims <- 1000  # global value for the whole script - increase to 100000 for final run, but note this takes around 16 hours to complete (depending on processor speed)

>>>>

nsims <- 100000  # global value for the whole script - increase to 100000 for final run, but note this takes around 16 hours to complete (depending on processor speed)
